Poincar\'e--Friedrichs constants over domains with shellable triangulations

### 2024-06-26 main.tex
clean up

\paragraph{Motivation}
We address the construction of potentials for the gradient, the curl and the divergence operators, and more generally the exterior derivative, over triangulated domains. The potential operators are ought to satisfy bounds in Lebesgue norms that are explicitly computable in terms of the geometry. 
In particular, these bounds on the operator norms yield computable upper bounds for Poincar\'e--Friedrichs inequalities. 
Equivalently, this gives lower bounds for the eigenvalues of several vector Laplacians.

@@

Finding a potential operator, whether it be linear or nonlinear, and bounding the Poincar\'e--Friedrichs constant is generally not an easy undertaking. 
We address this topic in the special case where $\Omega$ admits a shellable triangulation.
Even though only contractible domains can ever admit a shellable triangulation, 
having computable upper bounds for such domains is an important step stone towards the more general case. 
For example, local patches around a simplex within a larger triangulation are shellable.
\\

\paragraph{Background and literature review}

We take the Poincar\'e--Friedrichs inequality for the gradient of scalar functions as a conceptual point of reference.
Given a domain $\Omega \subseteq \bbR^{n}$ and $1 \leq p \leq \infty$,
we search for a constant $C > 0$ such that 
\begin{align*}
    \min\limits_{c\in\bbR}
    \| u - c \|_{L^{p}(\Omega)}
    \leq 
    C_{\grad,p} \| \nabla u \|_{L^p(\Omega)},
    \quad 
    u \in W^{1,p}(\Omega)
    .
\end{align*}
Finding a potential of a given gradient $\nabla u$ is generally a nonlinear operation. 
The operator norm of any \emph{linear} potential construction is an upper bound for the Poincar\'e--Friedrichs constant. 
Even though the existence of such a bounded linear potential construction is not evident a priori, 
picking the average-free potential 
\begin{align*}
    \Phi_{\grad}( \bff ) 
    := 
    \argmin\limits_{ \substack{ v \in W^{1,p}(\Omega) \\ \int_\Omega v = 0 } } \| \nabla v - \bff \|_{L^{p}(\Omega)},
    \quad 
    \bff \in \nabla W^{1,p}(\Omega)
\end{align*}
is a linear operation. Its operator norm is the constant in the Poincar\'e inequality 
\begin{align*}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    C_{\rm P} \| \nabla u \|_{L^p(\Omega)},
    \quad 
    u \in W^{1,p}(\Omega)
    ,
\end{align*}
where $u_\Omega$ denotes the average of $u$.
Considerable research effort has gone into finding (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities or Poincar\'e inequalities.

The situation is less clear cut when we study the curl or divergence operators
\begin{align*}
    \curl : \bfW^{p}(\curl,\Omega) \rightarrow \bfL^{p}(\curl,\Omega),
    \qquad 
    \divergence : \bfW^{p}(\divergence,\Omega) \rightarrow L^{p}(\Omega),
\end{align*}
where we use the function spaces
\begin{align*}
    \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in \bfL^p(\Omega) : \curl \bfu \in \bfL^p(\Omega) \right\}
    ,
    \\
    \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in \bfL^p(\Omega) : \divergence \bfu \in L^p(\Omega) \right\}
    .
\end{align*}
The fundamental difference is that the curl and divergence have infinite-dimensional kernels. 
In the Banach space case, it is not immediately evident that the kernels of these operators are complemented.
{\color{red}The existence of a bounded linear potential operator is a non-trivial fact even in the Hilbert space case. }
We are interested in constants for inequalities such as 
\begin{align*}
    \argmin\limits_{ \substack{ v \in W^{p}(\curl,\Omega) \\ \curl v = \bff } } \| v \|_{L^{p}(\Omega)}
    \leq 
    C_{\curl}
    \| \bff \|_{L^{p}(\Omega)}
    ,
    \qquad 
    \argmin\limits_{ \substack{ v \in W^{p}(\divergence,\Omega) \\ \divergence v = f } } \| v \|_{L^{p}(\Omega)}
    \leq 
    C_{\divergence}
    \| f \|_{L^{p}(\Omega)}
    ,
\end{align*}
and whether these constants can be estimated by the operator norm of linear potential operators 
\begin{align*}
    \Phi_{\curl} : \curl \bfW^{p}(\curl,\Omega) \rightarrow \bfW^{p}(\curl,\Omega)
    ,
    \quad 
    \Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow \bfW^{p}(\divergence,\Omega)
    .
\end{align*}
We remark that seemingly not much attention has been given to the study of optimal constants in such Poincar\'e--Friedrichs inequalities for the curl and divergence operators, 
% even if the domain is convex, 
which is in sharp contrast to the study of the gradient operator.

We explore formulate our main results in the framework of exterior calculus.
The formalism of exterior calculus generalizes vector calculus to arbitrary dimensions and allows us to study many differential operators, such as the curl and divergence, in a unified manner. 
%
It is used ubiquitously in physics and engineering. 
%
For the purpose of our discussion, this formalism allows us to leverage results from a larger body of literature in differential geometry and functional analysis. 
\\

\paragraph{Review literature}
Before we outline the main results of this exposition in more details, 
we first review the state of the literature on Poincar\'e--Friedrichs inequalities on specific classes of domains.

% Convex domains

% Domains star-shaped with respect to a ball

% Limitations

Most research on optimal constants has addressed the case of convex domains. 
Here, the optimal constants, in terms of the domain diameter alone, are known if $p=2$ \cite{bebendorf2003note} and if $p=1$ \cite{acosta2004optimal}. 
Notably, the optimal constants $C_{\grad,p}$ for all $1 \leq p < \infty$, again in terms of only the domain diameter, are known when the domain is convex.~\cite{esposito2013poincare,ferone2012remark}.

In the Hilbert space setting when $p = 2$, Guerini and Savo~\cite{guerini2004eigenvalue} have develop lower bounds for the spectrum of the Hodge--Laplace operator, which implies upper bounds for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence for the curl and divergence operators.
\\

While it is known that finite element patches admit Poincar\'e--Friedrichs inequalities, 
we are not aware of computable estimates. 
Clearly, not all local patches describe convex subdomains. 
An ostensibly more practical class of domains are domains star-shaped with respect to a ball.
Indeed, finite element patches of Lipschitz satisfy that condition. 
Over patches around interior subsimplices, the size of interior ball only depends on the shape regularity of the triangulation. However, the interior ball can be arbitrarily small when the patch is around a boundary simplex at a re-entrant corner, even if the mesh has good shape-regularity. 
Some interesting limit cases include the slit domain and the crossed bricks domain,
for which some finite element patches are not star-shaped with respect to any ball.

An open set star-shaped with respect to a internal point is also star-shaped with respect to some open ball within the domain.
We refer to \cite{hurri1988poincare} for that perspective.

The literature is much scarcer when it comes to this. 
We are aware of work by Guerini and Savo who estimate the Poincar\'e--Friedrichs constants over convex domains in the Hilbert space setting, when $p=2$, subject to no boundary conditions.
By duality, that implies lower bounds for the case of full boundary conditions.
We remark that their work also shows that over convex domains in 3D:
\begin{align*}
    C_{\grad} \geq C_{\curl} \geq C_{\divergence}.
\end{align*}
But we need to find potentials over a simplex subject to partial boundary conditions 
and we want to address the entire $1 \leq p \leq \infty$ of Lebesgue exponents. 
The existence of such potentials is well-known yet we are not aware of any explicit constants in the literature.

@@

It is often very helpful if a simplicial complex can be created recursively, starting with a single simplex. 
In particular, this enables the inductive method of proof.

@@

Whenever $T$ is an $n$-dimensional simplex 
\begin{align*}
    \kappa(T)
    := 
    \frac{ \diam(T)^{n} }{ n! \vol(T) }
    .
\end{align*}
Moreover, when $\calT$ is an $n$-dimensional simplicial complex, we introduce 
\begin{align*}
    \kappa(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa(T),
%     \qquad 
%     \delta(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \diam(T) }{ \diam(T') },
    \qquad 
    \rho(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \vol(T) }{ \vol(T') }.
\end{align*}
Whenever $S,T$ are two $n$-simplices that are a common face $F$ of codimension $1$, we let $\Xi_{S,T} : S \rightarrow T$ denote the affine diffeomorphism 
that preserves $F$. We define 
\begin{align*}
    \xi(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \| \Xi_{S,T} \|.
\end{align*}
This indicator quantifies how much reflection across the shared face distorts the geometry.

% and $\Phi : \Delta^{n} \rightarrow T$ is an affine diffeomorphism from the reference simplex,
% we define the quantity 
% \begin{align*}
%     \kappa(T)
%     := 
%     \frac{ \diam(T)^{n} }{ n! \vol(T) }
%     .
% \end{align*}

\begin{lemma}\label{lemma:affinetransform}
    Let $T$ be an $n$-simplex and let $\Phi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism. Then 
    \begin{align*}
        \| \Jacobian \Phi \|
        \leq 
        \sqrt{n} \cdot \diam(T)
        ,
        \qquad 
        \| \Jacobian \Phi^{-1} \|
        \leq 
        \sqrt{2n^{n}} 
        % \frac{ n! \vol(T) } { \diam(T)^{n} }
        \kappa(T)^{-1}
        \diam(T)^{-1}
        .
    \end{align*}
\end{lemma}
\begin{proof}
    We easily verify the first inequality. To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of $\Jacobian\Phi$ in descending order.
    Then $\sigma_1/\sigma_n \leq \sigma_1^{n} / \det(\Jacobian\Phi)$. Hence 
    \[
        \diam(T) 
        \leq 
        \sqrt{2} \sigma_1 
        \leq 
        \sqrt{2} 
        \frac{ \sigma_1^{n} }{ \det(\Jacobian\Phi) } 
        \sigma_n
        \leq 
        \sqrt{2n^{n}} 
        \frac{ \diam(T)^{n} }{ n! \vol(T) } 
        \sigma_n
        .
    \]
    The desired result is thus evident. 
\end{proof}

@@

\begin{lemma}\label{lemma:poincarefriedrichsoverfacepatch}
    Suppose that $T, T'$ are two $n$-simplices whose intersection is a common face $F := T_1 \cap T_2$. Then 
    \begin{align*}
        \min\limits_{ c \in \bbR }
        \| u - c \|_{L^{p}(U)}
        &
        \leq 
        2 C_{\rm{EFNT},p}
        \max\left( 
            \frac{ \vol(T_1) }{ \vol(T_2) }
            ,
            \frac{ \vol(T_2) }{ \vol(T_1) }
        \right)^{\frac 1 p}
        \max\left( \diam(T_1), \diam(T_2) \right)
        \| \nabla u \|_{L^{p}(U)}
        \\&
        \leq 
        2 C_{\rm{EFNT},p}
        \rho(\calT)^{\frac 1 p}
        \max\left( \diam(T_1), \diam(T_2) \right)
        \| \nabla u \|_{L^{p}(U)}
        .
    \end{align*}
    for any $u \in W^{1,p}(\Omega)$ with $p \in [1,\infty]$.
\end{lemma}
\begin{proof}
    Let $\hat T_1$ be the $n$-simplex whose vertices $v_0=0, v_1=e_1, \dots, v_{n-1} = e_{n-1}, v_n = e_n$ are the origin and the $n$ canonical unit vectors. 
    We let $\hat T_2$ be the $n$-simplex whose vertices are $v_0=0, v_1=e_1, \dots, v_{n-1} = e_{n-1}, v'_n = -e_n$. 
    Write $U := T_1 \cup T_2$ and $\hat U := \hat T_1 \cup \hat T_2$.
    We fix affine homeomorphisms $\Phi_1 : \hat T_1 \rightarrow T_1$ and $\Phi_2 : \hat T_2 \rightarrow T_2$
    which map the convex closure of $v_0, \dots, v_{n-1}$ onto the common face $F$.
    Note that these affine transformations define a bi-Lipschitz mapping $\Phi : \hat U \rightarrow U$.

>>>>

We address the construction of potentials for the gradient, the curl and the divergence operators, and more generally the exterior derivative, over triangulated domains. The potential operators are ought to satisfy bounds in Lebesgue norms that are explicitly computable in terms of the geometry. 
In particular, these bounds on the operator norms yield computable upper bounds for Poincar\'e--Friedrichs inequalities. 
Equivalently, this gives lower bounds for the eigenvalues of several vector Laplacians.

@@

Finding a potential operator, whether it be linear or nonlinear, and bounding the Poincar\'e--Friedrichs constant is generally not an easy undertaking. 
We address this topic in the special case where $\Omega$ admits a shellable triangulation.
Even though only contractible domains can ever admit a shellable triangulation, 
having computable upper bounds for such domains is an important step stone towards the more general case. 
For example, local patches around a simplex within a larger 2D or 3D triangulation are shellable.
We express all our main results in the calculus of differential forms, also known as exterior calculus, 
and state the instances of the curl and divergence operator as special cases. 
\\

Before we outline the main results of this exposition in more details, 
we first review the state of the literature on Poincar\'e--Friedrichs inequalities on specific classes of domains. 
We take the Poincar\'e--Friedrichs inequality for the gradient of scalar functions as a conceptual point of reference.
Given a domain $\Omega \subseteq \bbR^{n}$ and $1 \leq p \leq \infty$,
we search for a constant $C > 0$ such that 
\begin{align*}
    \min\limits_{c\in\bbR}
    \| u - c \|_{L^{p}(\Omega)}
    \leq 
    C_{\grad,p} \| \nabla u \|_{L^p(\Omega)},
    \quad 
    u \in W^{1,p}(\Omega)
    .
\end{align*}
Finding a potential of a given gradient $\nabla u$ is generally a nonlinear operation. 
The operator norm of any \emph{linear} potential construction is an upper bound for the Poincar\'e--Friedrichs constant. 
Even though the existence of such a bounded linear potential construction is not evident a priori, 
picking the average-free potential 
One example for a bounded linear operator is the average-free potential:
\begin{align*}
    \Phi_{\grad}( \bff ) 
    := 
    \argmin\limits_{ \substack{ v \in W^{1,p}(\Omega) \\ \int_\Omega v = 0 } } \| \nabla v - \bff \|_{L^{p}(\Omega)},
    \quad 
    \bff \in \nabla W^{1,p}(\Omega)
    .
\end{align*}
Its operator norm is the constant in the Poincar\'e inequality 
\begin{align*}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    C_{\rm P} \| \nabla u \|_{L^p(\Omega)},
    \quad 
    u \in W^{1,p}(\Omega)
    ,
\end{align*}
where $u_\Omega$ denotes the average of $u$.
Considerable research effort has gone into finding (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities or Poincar\'e inequalities.

Most research on optimal constants has addressed the case of convex domains. 
Here, the optimal constants, in terms of the domain diameter alone, are known if $p=2$ \cite{bebendorf2003note} and if $p=1$ \cite{acosta2004optimal}. 
Notably, the optimal constants $C_{\grad,p}$ for all $1 \leq p < \infty$, again in terms of only the domain diameter, are known when the domain is convex.~\cite{esposito2013poincare,ferone2012remark}.
When the domain is not convex but star-shaped with respect to a ball,
then a Poincar\'e inequality is already implicit in polynomial interpolation estimates that are known to the mathematical community~\cite{...}. 
An open set star-shaped with respect to a internal point is also star-shaped with respect to some open ball within the domain.
We refer to \cite{hurri1988poincare} for that perspective.

The situation is less clear cut when we study the curl or divergence operators in vector calculus.
Here, we use the function spaces
\begin{align*}
    \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in \bfL^p(\Omega) : \curl \bfu \in \bfL^p(\Omega) \right\}
    ,
    \\
    \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in \bfL^p(\Omega) : \divergence \bfu \in L^p(\Omega) \right\}
    .
\end{align*}
Their members are vector fields whose distributional partial derivatives satisfy certain cancellation properties. 
Our objective is to find bounded potentials for the operators 
\begin{align*}
    \curl : \bfW^{p}(\curl,\Omega) \rightarrow \bfL^{p}(\curl,\Omega),
    \qquad 
    \divergence : \bfW^{p}(\divergence,\Omega) \rightarrow L^{p}(\Omega),
\end{align*}
The fundamental difference is that the curl and divergence have infinite-dimensional kernels. 
In the Banach space case, it is not immediately evident that the kernels of these operators are complemented.
The existence of a bounded linear potential operator is a non-trivial fact even in the Hilbert space case.
We are interested in constants for inequalities such as 
\begin{align*}
    \argmin\limits_{ \substack{ v \in W^{p}(\curl,\Omega) \\ \curl v = \bff } } \| v \|_{L^{p}(\Omega)}
    \leq 
    C_{\curl}
    \| \bff \|_{L^{p}(\Omega)}
    ,
    \qquad 
    \argmin\limits_{ \substack{ v \in W^{p}(\divergence,\Omega) \\ \divergence v = f } } \| v \|_{L^{p}(\Omega)}
    \leq 
    C_{\divergence}
    \| f \|_{L^{p}(\Omega)}
    ,
\end{align*}
and whether these constants can be estimated by the operator norm of linear potential operators 
\begin{align*}
    \Phi_{\curl} : \curl \bfW^{p}(\curl,\Omega) \rightarrow \bfW^{p}(\curl,\Omega)
    ,
    \quad 
    \Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow \bfW^{p}(\divergence,\Omega)
    .
\end{align*}
Not much attention seems to have been given to the study of optimal constants in such Poincar\'e--Friedrichs inequalities for the curl and divergence operators. 
% even if the domain is convex, 
This sharply contrasts to the study of the gradient operator.

The literature is much scarcer when it comes to this. 
We can access some estimates from the literature in the formalism of exterior calculus. 
We are aware of work by Guerini and Savo who estimate the Poincar\'e--Friedrichs constants over convex domains in the Hilbert space setting, when $p=2$ and no boundary conditions are imposed. 
In the Hilbert space setting when $p = 2$, Guerini and Savo~\cite{guerini2004eigenvalue} have develop lower bounds for the spectrum of the Hodge--Laplace operator over convex domains. This implies upper bounds for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence for the curl and divergence operators.
By duality, that implies lower bounds for the case of full boundary conditions.
We remark that their work also shows that over convex domains in 3D:
\begin{align*}
    C_{\grad} \geq C_{\curl} \geq C_{\divergence}.
\end{align*}
% TODO: summarize 
When the domain is star-shaped with respect to a ball, then estimates for the Poincar\'e--Friedrichs constant 
follow from bounds on the operator norm of regularized Poincar\'e operators~\cite{costabel2010bogovskiui}
as mapping between Lebesgue spaces,
though these estimates have not been made explicit in the literature yet.
\\

While it is known that finite element patches admit Poincar\'e--Friedrichs inequalities, 
we are not aware of computable estimates for the case of $\bfH(\curl)$ and $\bfH(\divergence)$. % TODO
Clearly, not all local patches describe convex subdomains. 
One possible avenue towards Poincar\'e--Friedrichs constants is the observation that stars in triangulations are often star-shaped with respect to a ball. 
Over patches around interior subsimplices, the size of interior ball only depends on the shape regularity of the triangulation. 
However, the interior ball can be arbitrarily small when the patch is around a boundary simplex at a re-entrant corner, even if the mesh has good shape-regularity. 
Estimates that rely on this geometric condition deteriorate when the aforementioned ball has small radius,
and that is inevitable when the domain has a bad geometry. 
Some interesting limit cases include the slit domain and the crossed bricks domain,
for which some finite element patches are not star-shaped with respect to any ball.

Veeser and Verfürth have provided computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over finite element stars~\cite{veeser2000}.

% TODO:V&V seems to be the only reference for stars .... 
General results of this type for a class containing the finite element stars are not known to us. 
In particular and as will be illustrated in a moment, 
Poincaré constants of stars and thus of star-shaped domains may be arbitrarily large. 
Consequently, corresponding bounds have to incorporate some quantity that is sensible to the possible lack of
convexity.

There is a popular avenue towards estimates that is able to circumvent the effect of low boundary regularity. 
A common principle of many proofs is to construct a potential step-by-step: 
starting with a single triangle, the potential is constructed over an increasing subdomain, until the entire domain is complete. That procedure applies to general triangulated domains, not only local stars, though the latter is our main interest. 
The underlying idea is that we first construct a potential for the gradient over an initial simplex. 
Every time we have found a potential over a subdomain, we construct a potential over a neighboring simplex or patch:
along the intersection, the two potentials will only differ by a constant, 
and that difference can easily be removed. 
That difference can easily be removed. 
...
Estimates for Poincar\'e--Friedrichs constants of triangulated domains are known in various forms.
% TODO: list literature
% TODO: details 
\\

@@

It is often very helpful if a simplicial complex can be created recursively, starting with a single simplex. 
In particular, this enables the inductive method of proof.
% 
We explore formulate our main results in the framework of exterior calculus.
The formalism of exterior calculus generalizes vector calculus to arbitrary dimensions and allows us to study many differential operators, such as the curl and divergence, in a unified manner. 
%
It is used ubiquitously in physics and engineering. 
%
For the purpose of our discussion, this formalism allows us to leverage results from a larger body of literature in differential geometry and functional analysis.

But we need to find potentials over a simplex subject to partial boundary conditions 
and we want to address the entire $1 \leq p \leq \infty$ of Lebesgue exponents. 
The existence of such potentials is well-known yet we are not aware of any explicit constants in the literature.

The regularized Bogovskii potential operator was studied extensively by Costabel and McIntosh.
These operators are defiend over sets star-shaeped with respect to a ball. 
Their analysis identifies the potential as a pseudodifferential operator of negative order and utilizes tools of harmonic analysis. 
We study a variation of this potential operator over convex sets.
We simply use a constant averaging over the entire domain. 
While the resulting Bogovskii-type potential has more moderate regularity properties, 
this simplification suits our purposes and enables some simple estimates for the continuity constant of the potential operator in Lebesgue norms.

@@

Whenever $T$ is an $n$-dimensional simplex 
\begin{align}\label{math:geometricshapemeasure}
    \kappa(T)
    := 
    \frac{ \diam(T)^{n} }{ n! \vol(T) }
    .
\end{align}
Moreover, when $\calT$ is an $n$-dimensional simplicial complex, we introduce 
\begin{align}\label{math:moremeasures}
    \kappa(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa(T),
%     \qquad 
%     \delta(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \diam(T) }{ \diam(T') },
    \qquad 
    \rho(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \vol(T) }{ \vol(T') }.
\end{align}
Whenever $S,T$ are two $n$-simplices that are a common face $F$ of codimension $1$, we let $\Xi_{S,T} : S \rightarrow T$ denote the affine diffeomorphism 
that preserves $F$. We define 
\begin{align}\label{math:reflectionmeasure}
    \xi(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \| \Xi_{S,T} \|.
\end{align}
This indicator quantifies how much reflection across the shared face distorts the geometry.

% and $\varphi : \Delta^{n} \rightarrow T$ is an affine diffeomorphism from the reference simplex,
% we define the quantity 
% \begin{align*}
%     \kappa(T)
%     := 
%     \frac{ \diam(T)^{n} }{ n! \vol(T) }
%     .
% \end{align*}

\begin{lemma}\label{lemma:affinetransform}
    Let $T$ be an $n$-simplex and let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism. Then 
    \begin{align*}
        \| \Jacobian \varphi \|
        \leq 
        \sqrt{n} \cdot \diam(T)
        ,
        \qquad 
        \| \Jacobian \varphi^{-1} \|
        \leq 
        \sqrt{2n^{n}} 
        % \frac{ n! \vol(T) } { \diam(T)^{n} }
        \kappa(T)^{-1}
        \diam(T)^{-1}
        .
    \end{align*}
\end{lemma}
\begin{proof}
    We easily verify the first inequality. To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of $\Jacobian\varphi$ in descending order.
    Then $\sigma_1/\sigma_n \leq \sigma_1^{n} / \det(\Jacobian\varphi)$. Hence 
    \[
        \diam(T) 
        \leq 
        \sqrt{2} \sigma_1 
        \leq 
        \sqrt{2} 
        \frac{ \sigma_1^{n} }{ \det(\Jacobian\varphi) } 
        \sigma_n
        \leq 
        \sqrt{2n^{n}} 
        \frac{ \diam(T)^{n} }{ n! \vol(T) } 
        \sigma_n
        .
    \]
    The desired result is thus evident. 
\end{proof}

@@

\begin{lemma}\label{lemma:poincarefriedrichsoverfacepatch}
    Suppose that $T, T'$ are two $n$-simplices whose intersection is a common face $F := T_1 \cap T_2$. Then 
    \begin{align*}
        \min\limits_{ c \in \bbR }
        \| u - c \|_{L^{p}(U)}
        &
        \leq 
        2 C_{\rm{EFNT},p}
        \max\left( 
            \frac{ \vol(T_1) }{ \vol(T_2) }
            ,
            \frac{ \vol(T_2) }{ \vol(T_1) }
        \right)^{\frac 1 p}
        \max\left( \diam(T_1), \diam(T_2) \right)
        \| \nabla u \|_{L^{p}(U)}
        \\&
        \leq 
        2 C_{\rm{EFNT},p}
        \rho(\calT)^{\frac 1 p}
        \max\left( \diam(T_1), \diam(T_2) \right)
        \| \nabla u \|_{L^{p}(U)}
        .
    \end{align*}
    for any $u \in W^{1,p}(\Omega)$ with $p \in [1,\infty]$.
\end{lemma}
\begin{proof}
    Let $\hat T_1$ be the $n$-simplex whose vertices $v_0=0, v_1=e_1, \dots, v_{n-1} = e_{n-1}, v_n = e_n$ are the origin and the $n$ canonical unit vectors. 
    We let $\hat T_2$ be the $n$-simplex whose vertices are $v_0=0, v_1=e_1, \dots, v_{n-1} = e_{n-1}, v'_n = -e_n$. 
    Write $U := T_1 \cup T_2$ and $\hat U := \hat T_1 \cup \hat T_2$.
    We fix affine homeomorphisms $\varphi_1 : \hat T_1 \rightarrow T_1$ and $\varphi_2 : \hat T_2 \rightarrow T_2$
    which map the convex closure of $v_0, \dots, v_{n-1}$ onto the common face $F$.
    Note that these affine transformations define a bi-Lipschitz mapping $\varphi : \hat U \rightarrow U$.

    Suppose that $u \in W^{1,p}(U)$. Then $\hat u := u \circ \varphi \in W^{1,p}(\hat U)$. 
    We observe 
    \begin{align*}
        \| \nabla \hat u \|_{L^{p}(\hat U)}^{p}
        &=
        \| \nabla \hat u \|_{L^{p}(\hat T_1)}^{p}
        +
        \| \nabla \hat u \|_{L^{p}(\hat T_2)}^{p}
        \\&
        \leq 
        |\det(\Dif \varphi_1)|
        \cdot \| \Dif \varphi_1 \|^{p}
        \cdot 
        \| \nabla u \|_{L^{p}(T_1)}^{p}
        +
        |\det(\Dif \varphi_2)|
        \cdot \| \Dif \varphi_2 \|^{p}
        \cdot 
        \| \nabla u \|_{L^{p}(T_2)}^{p}
        \\&
        \leq 
        \max\left( 
            |\det(\Dif \varphi_1)|^{-1} \cdot \| \Dif \varphi_1 \|^{p}
            ,
            |\det(\Dif \varphi_2)|^{-1} \cdot \| \Dif \varphi_2 \|^{p}
        \right)
        \| \nabla u \|_{L^{p}(U)}^{p}
        .
    \end{align*}
    Hence 
    \begin{align*}
        \| \nabla \hat u \|_{L^{p}(\hat U)}
        &\leq 
        \max\left( 
            |\det(\Dif \varphi_1)|^{-\frac 1 p} \cdot \| \Dif \varphi_1 \|
            ,
            |\det(\Dif \varphi_2)|^{-\frac 1 p} \cdot \| \Dif \varphi_2 \|
        \right)
        \| \nabla u \|_{L^{p}(U)}
        .
    \end{align*}
    There exists $\hat w \in W^{1,p}(U)$ such that $\nabla \hat w = \nabla \hat u$ and 
    \begin{align*}
        \| \hat w \|_{L^{p}(\hat U)}
        \leq 
        2 C_{\rm{EFNT},p}
        \| \nabla \hat u \|_{L^{p}(\hat U)}
        .
    \end{align*}
    Next, setting $w = \hat w \circ \varphi^{-1}$, we find $\nabla w = \nabla u$ and 
    \begin{align*}
        \| w \|_{L^{p}(U)}
        \leq 
        \max\left( 
            |\det(\Dif \varphi_1)|
            ,
            |\det(\Dif \varphi_2)|
        \right)^{\frac 1 p}
        \| \hat w \|_{L^{p}(\hat U)}
        .
    \end{align*}
    Abbreviate $D := \max\left( \diam(T_1), \diam(T_2) \right)$. In combination, 
    \begin{align*}
        \| w \|_{L^{p}(U)}
        &\leq 
        2 C_{\rm{EFNT},p}
        \max\left( 
            |\det(\Dif \varphi_1)|
            ,
            |\det(\Dif \varphi_2)|
        \right)^{\frac 1 p}
        \max\left( 
            |\det(\Dif \varphi_1)|^{-\frac 1 p} 
            ,
            |\det(\Dif \varphi_2)|^{-\frac 1 p} 
        \right)
        D
        \| \nabla u \|_{L^{p}(U)}
        \\&
        \leq 
        2 C_{\rm{EFNT},p}
        \max\left( 
            |\det(\Dif \varphi_1)|
            ,
            |\det(\Dif \varphi_2)|
        \right)^{\frac 1 p}
        \min\left( 
            |\det(\Dif \varphi_1)|
            ,
            |\det(\Dif \varphi_2)| 
        \right)^{-\frac 1 p} 
        D
        \| \nabla u \|_{L^{p}(U)}
        \\&
        \leq 
        2 C_{\rm{EFNT},p}
        \max\left( 
            \frac{ |\det(\Dif \varphi_1)| }{ |\det(\Dif \varphi_2)| }
            ,
            \frac{ |\det(\Dif \varphi_2)| }{ |\det(\Dif \varphi_1)| }
        \right)^{\frac 1 p}
        D
        \| \nabla u \|_{L^{p}(U)}
        \\&
        \leq 
        2 C_{\rm{EFNT},p}
        \max\left( 
            \frac{ \vol(T_1) }{ \vol(T_2) }
            ,
            \frac{ \vol(T_2) }{ \vol(T_1) }
        \right)^{\frac 1 p}
        D
        \| \nabla u \|_{L^{p}(U)}
        .
    \end{align*}
    This gives the desired result. 
\end{proof}
